BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-11-21 tex/3-algorithms.tex
Algorithm 2 done.

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
% HTML extraction is non trival
Extracting metadata and content from HTML is not easy. Standards and recommendations have been present for quite some time, and strict specify how HTML documents should be organized. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}. In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{id} or \code{class} attributes to organize HTML pages. Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.

% Assumptions when working with blogs
\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed than most of the failing blogs are violating one of these assumptions.}

With web blogs as our target websites we made the following assumptions\Anote{assumptions} that will be central in our extraction procedure:
n procedure:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds that give a structured and standardized view of the blogs most recent posts,
  \item\label{similarhtmlAssum} Posts of a same blog share a similar HTML structure.
\end{enumerate}
On average, web feeds only contain about 20 entries\cite{oita2010}, less than the total number of posts in an average blog. Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
% Per blog procedure, related work
In order to extract content, authors, date and comments of posts of a blog, we will proceed by first building extraction rules from the information given on it's web feed. These rules will take advantage of the similarities between HTML structure of pages on a same blog in order to be applicable to all posts of a blog. The approach is not new and has already showed to give great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that works directly on HTML pages, without the need for a web feed.

@@

% Algorithm, inputs/output
Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for content of blog posts. It takes as input a set of pairs of HTML pages and target contents, and returns an extraction rule. This rule should be such that when applied to one of the input pages, the extracted text is close to the corresponding target content.

% General comment, embarrassingly parallel
The idea is quite simple: compute the best extraction rule for each page/target pair and return the most frequent best rule. Making each of these computation independent might seems like a lose of information compared to alternative solutions such as having a global score for each rule computed as the average of it's score over all pages of the feed. We observed in our tests several cases were the independent solution performs better. When the web feed has a large portion of posts with very few text, mean based solutions tend to be more influenced by these outliers and are inclined to return wrong results with constant low scores. In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivialy be executed by multiple threads.

% Input from assumptions.
Given a blog, the crawler can use assumption \ref{havefeedAssum} to obtain inputs for Algorithm \ref{extractionAlgo}. Indeed a web feeds provide either a textual content or a textual description for each of it's entries, as well as a link to the corresponding page. Assumptions \ref{similarhtmlAssum} suggests the existence of solution: an extraction rule appropriate for each input pages/target content pairs. \ref{similarhtmlAssum} is also key to ensure applicability of the rule to all posts of the blog.

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
% XPath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{Apply} function use Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over \code{id} attribute, selection over \code{class} attribute and selection with absolute path. We have found that ignoring nodes without \code{id} or \code{class} absolutes prunes out a lot of uninteresting HTML nodes without decreasing  the quality of the result. Also when both \code{id} and \code{class} attributes are present the \code{id} attribute shows to be a stronger selector, here matching the HTML specification regarding the uniqueness of \code{id}. This observations led to the following \coderef{allrulesAlgo} function:

@@

% String similarity
Unsurprisingly, the choice of string similarity has a strong influence on the running time and precision of the extraction procedure. We use Sørensen–Dice coefficient similarity\cite{dice1945}, which is to the best of our knowledge the only string similarity fulfilling the following criteria:

@@

The Sørensen–Dice coefficient methods operates by first building sets of pairs of adjacent characters, also knows as \emph{Bigrams}, and then applying the \emph{quotient of similarity} formula:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time complexity, linear reformulation}

% Algo 1 is quadratic
With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time. Let's first assume that we have at our disposal a linear time HTML parser which builds an appropriate data-structure indexed on \code{id} and \code{class} attributes, effectively making \code{Apply} $\in$ \Oof{1}. As stated before, the outer loop splits the input into independent computations, and each call to \coderef{allrulesAlgo} returns less rules than the number of nodes in HTML tree, in linear time. Therefor, the body of the inner loop will be executed a linear number of time. Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} will run in \Oof{n}, leading to an overall quadratic running time.

% Linera reformulation
There is a reformulation of Algorithm \ref{extractionAlgo} with linar running time. As you will see, it requiers to break the separation in annex functions by bringing string similariy and HTML tree traversal logic into the core of the algorithm. It works like this

@@

-> (algo)
-> complecity analisis

The reason we presented Algorithm \ref{extractionAlgo} and

While caching the bigram computation of target gives a speed up

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for comments and authors}
- comments
- date authors

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation}
\comment{HTML extraction is non trival}%
Extracting metadata and content from HTML is not easy. Standards and recommendations have been present for quite some time, strictly specifying how HTML documents should be organized. For instance the \code{<h1></h1>} tags should contain the highest-level heading of the page and must not appear more than once per page\cite{w3c2002}. More recently, specifications such as Microdata\cite{whatwg2013} define ways to nest semantics and metadatas inside HTML documents, but as of today suffer from very low usage rates, under 0.5\%\cite{andrewrogers2013}. In fact, a majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} containers with custom \code{id} or \code{class} attributes to organize pages, and it is not uncommon to enconter incorrect HTML. Under such consistences, relying on HTML structure to extract data from web pages it's not viable and other techniques have to be employed.

\Anotecontent{assumptions}{Our experiments on a large dataset of blogs showed than most of the failing blogs are violating one of these assumptions.}

\comment{Assumptions when working with blogs}%
With web blogs as our target websites we made the following assumptionsthat will play a central role in our extraction procedure\Anote{assumptions}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: a structured and standardized view of blogs most recent posts,
  \item\label{similarhtmlAssum} Posts of a same blog share a similar HTML structure.
\end{enumerate}
Usually, web feeds only contain about 20 entries\cite{oita2010}, less than the total number of posts in an average blog. Consequently, in order to effectively archive old content from blogs it is necessary to download and process pages beyond the one referenced by the feed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Content extraction}
\comment{Per blog procedure, related work}%
In order to extract content, authors, date and comments of posts of a blog, we will proceed by first building extraction rules from the information given on it's web feed. These rules will take advantage of the similarities between HTML structure of pages on a same blog in order to be applicable to all posts of a blog. The approach is not new and has already showed to give great results (see \cite{gkotsis2013}, \cite{oita2010}), outperforming more generic extraction algorithms that works directly on HTML pages, without the need for a web feed.

@@

\comment{Algorithm, inputs/output}%
Algorithm \ref{extractionAlgo} shows the procedure we use to build the extraction rule for content of blog posts. It takes as input a set of pairs of HTML pages and target contents, and returns an extraction rule. This rule should be such that when applied to one of the input pages, the extracted text is close to the corresponding target content.

\comment{General comment, embarrassingly parallel}%
The idea is quite simple: compute the best extraction rule for each page/target pair and return the most frequent best rule. Making each of these computation independent might seems like a lose of information compared to alternative solutions such as having a global score for each rule computed as the average of it's score over all pages of the feed. We observed in our tests several cases were the independent solution performs better. When the web feed has a large portion of posts with very few text, mean based solutions tend to be more influenced by these outliers and are inclined to return wrong results with constant low scores. In addition, having a independent computation for each input makes the algorithm \emph{embarrassingly parallel}: iterations of the outer loop can trivialy be executed by multiple threads.

\comment{Input from assumptions.}%
Given a blog, the crawler can use assumption \ref{havefeedAssum} to obtain inputs for Algorithm \ref{extractionAlgo}. Indeed a web feeds provide either a textual content or a textual description for each of it's entries, as well as a link to the corresponding page. Assumptions \ref{similarhtmlAssum} suggests the existence of solution: an extraction rule appropriate for each input pages/target content pairs. \ref{similarhtmlAssum} is also key to ensure applicability of the rule to all posts of the blog.

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
\comment{XPath selectors (id, else class, else path)}%
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used parse html pages and apply extraction rules, thus providing the \code{Apply} function use Algorithm \ref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over \code{id} attribute, selection over \code{class} attribute and selection with absolute path. We have found that ignoring nodes without \code{id} or \code{class} absolutes prunes out a lot of uninteresting HTML nodes without decreasing  the quality of the result. Also when both \code{id} and \code{class} attributes are present the \code{id} attribute shows to be a stronger selector, here matching the HTML specification regarding the uniqueness of \code{id}. This observations led to the following \coderef{allrulesAlgo} function:

@@

\comment{String similarity}%
Unsurprisingly, the choice of string similarity has a strong influence on the running time and precision of the extraction procedure. We use Sørensen–Dice coefficient similarity\cite{dice1945}, which is to the best of our knowledge the only string similarity fulfilling the following criteria:

@@

The Sørensen–Dice coefficient methods operates by first building sets of pairs of adjacent characters, also knows as \emph{bigram}, and then applying the \emph{quotient of similarity} formula:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Time complexity and linear reformulation}

\comment{Algo 1 is quadratic}%
With both \coderef{allrulesAlgo} and \coderef{similarityAlgo} function defined, we will now show that Algorithm \ref{extractionAlgo} has a quadratic running time. Let's first assume that we have at our disposal a linear time HTML parser which builds an appropriate data-structure indexed on \code{id} and \code{class} attributes, effectively making \code{Apply} $\in$ \Oof{1}. As stated before, the outer loop splits the input into independent computations, and each call to \coderef{allrulesAlgo} returns less rules than the number of nodes in HTML tree, in linear time. Therefor, the body of the inner loop will be executed a linear number of time. Because extraction rule can return arbitrary subtrees of the queried page, each call to \coderef{similarityAlgo} will run in \Oof{n}, leading to an overall quadratic running time.

\comment{Linear reformulation}%
We will now present Algorithm \ref{linearAlgo}, a dynamic programming reformulation of Algorithm \ref{extractionAlgo} with linear running time. While very intuitive, the original idea of first generating extraction rules and then picking these best rule prevents an effective reuse of previously computed bigrams. For instance, when evaluating the extraction rule for the HTML root node, Algorithm \ref{extractionAlgo} will obtain the complete string of the page and pass it to the \ref{similarityAlgo} function. At this point, the information of where the string could be spitted into substring with already computed bigrams is not accessible, and the bigram of the page has to be computed by linearly traversing the full string. To overcome this limitation and implement an effective memoization \comment{without R!}over the bigram computations, Algorithm \ref{linearAlgo} uses a post-order traversal of the HTML tree to compute node bigram from it's children bigrams, effectively avoiding a complete string serialization.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Variations for comments, dates and authors}
- comments
- date authors

### 2013-11-21 tex/4-techniques.tex
Linear algo started.
Algorithm 2 done.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
% Introduction
JavaScript is a widely used use language for client-side web scripting. While some applications simply use it for aesthetics aspects such as menus and animations, an increasing number of websites use JavaScript to download and display content. In such circumstances, traditional HTML based crawled would not see the web site as it would be presented to a human visitor and might therefore be obsolete for extracting data from the page.

% Motivation
In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation. The most frequent cases where blogs using the Disqus\cite{disqus2013} and LiveFyre\cite{livefyre2013} comment hosting services. These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users. Less commonly, some blogs are fully rendered using JavaScript. Concretely, when loading such website the web browser will not receive the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content. On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \cite{antinharasymiv2011} that use this mechanism.

% The solution
To support blogs with JavaScript generated content we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. In order to take full advantage of all the extraction functionalities, the JavaScript rendering is done as the very first step of blog post processing. This way, every other part of the project is independent of whether or not the page its currently processing was actually rendered by PhantomJS or comes directly from the web server. Extracting blog post content, comments and images therefore works equally well on both blogs with JavaScript generated content and traditional HTML blogs.

% Click click scripting
In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities. When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons. As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded. As you will see in the evaluation section, \TODO{we will see..}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
  \caption{Overview of the crawler architecture.}
  \label{architecture}
\end{figure}

Our project is build on top of Scrapy\cite{scrapy2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modulable high-level architecture which we followed in our implementation of the BlogForever Crawler. As illustrated in Figure~\ref{architecture}, Scrapy is divided in several components: \emph{Spiders}, \emph{Item Pipeline}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}, where each of can be used to implement a different functionality.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
% Into, blog-post identification
In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

% download priority heuristic
In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient. Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next. Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken it into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{JavaScript rendering}
\comment{Introduction}%
JavaScript is a widely used use language for client-side web scripting. While some applications simply use it for aesthetics aspects such as menus and animations, an increasing number of websites use JavaScript to download and display content. In such circumstances, traditional HTML based crawled would not see the web site as it would be presented to a human visitor and might therefore be obsolete for extracting data from the page.

\comment{Motivation}%
In our specific use case of crawling the blog sphere, we encountered several blogs where data was missed because of the lack of JavaScript interpretation. The most frequent cases where blogs using the Disqus\cite{disqus2013} and LiveFyre\cite{livefyre2013} comment hosting services. These tools are very handy to setup for webmasters because the entire comments infrastructure is externalized and the setup essential comes down to including a JavaScript snippet in the target web page. Both of these services heavily rely on JavaScript to download and display the comments, even providing functionalities such as real-time update of comments there are written by users. Less commonly, some blogs are fully rendered using JavaScript. Concretely, when loading such website the web browser will not receive the page content inside an HTML page, but will instead have to execute a script containing the procedure to download and display the page content. On example can be found on the Blogger platforms which proposes as one of its default templates the \emph{Dynamic Views} \cite{antinharasymiv2011} that use this mechanism.

\comment{The solution}%
To support blogs with JavaScript generated content we embed a full web browser into the crawler. After considering multiple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performances and scripting capabilities. In order to take full advantage of all the extraction functionalities, the JavaScript rendering is done as the very first step of blog post processing. This way, every other part of the project is independent of whether or not the page its currently processing was actually rendered by PhantomJS or comes directly from the web server. Extracting blog post content, comments and images therefore works equally well on both blogs with JavaScript generated content and traditional HTML blogs.

\comment{Click click scripting}%
In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities. When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a \emph{Show More Comments} buttons. As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded. As you will see in the evaluation section, \TODO{we will see..}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.47\textwidth]{img/scrapy_architecture.png}
  \caption{Overview of the crawler architecture.\TODO{Source}}
  \label{architecture}
\end{figure}

Our project is build on top of Scrapy\cite{scra py2013}, an open source Python framework for web crawling. Scrapy provide an elegant and modulable high-level architecture which we followed in our implementation of the BlogForever Crawler. As illustrated in Figure~\ref{architecture}, Scrapy is divided in several components: \emph{Spiders}, \emph{Item Pipeline}, \emph{Downleader Middlewares} and \emph{Spider Middlewares}, where each of can be used to implement a different functionality.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}
\comment{Into, blog-post identification}%
In order to find and identify blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog-post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last in first out} manner. The \emph{blog-post identification} function is able to identify from a URL whether or not the corresponding page is a blog-post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

\comment{download priority heuristic}%
In order to efficiently deal with blogs with a large number non-blog-post pages, this blog-post identification mechanism is not sufficient. Indeed, after all pages identified as blog-post are processed, the crawler needs to download non-blog-post pages to search for additional blog-posts. To replace the naive random walk, depth first search or breadth first search web site traversals, we use a priority queue where new URL priorities are determined using a simple machine learning algorithm. Given an URL, the machine learning system does an estimation on the number of links to blog-post the corresponding page will contain. This estimated number of links are then used as a \emph{download priorities} to decide the best URL to visite next. Each time a page is effectively downloaded, the actual number of blog-post links it contains is computed and passed to the machine learning system as training data that will then be taken it into account during future predictions. This mechanism has shown to be indispensable for blogs hosting on the single domain a large number of non-blog web pages, such as a forum or a wiki.
